---
title: "Freezers analyzes for FreezerPro import"
author: "Nolwenn Lavielle"
date: "23 août 2016"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## File informations

```{r loaddataL}
path <- "/Volumes/LabExMI/Users/Nolwenn/FreezerPro/DataToImport/"
filename <- "freezers.csv"
df.samples <- read.csv(file = paste(path, filename, sep =""), 
                       header=TRUE, sep=',', stringsAsFactors = FALSE)
```

QC of a file generated to import Freezers information into FreezerPro.

* **Filename**: `r filename`
  + **file creation date:** 2016-08-23
  + **number of rows:** `r nrow(df.samples)`
  + **number of columns:** `r ncol(df.samples)`
  + **column names:** `r names(df.samples)`

## Data informations

### Number of boxes per freezer:

Expect each Freezer is assign to it respective barcode.

```{r freezerinfo}
result <- data.frame(table(df.samples[,c("Freezer")]))
colnames(result) <- c("Freezer", "Number of boxes")
pander::pander(result)
```

***Comments***:

* first line, freezer name
* second line, number of boxes
* there is no column *FreezerBarcode* because this file will be used to generate Freezers in FreezerPro software

### Number of boxes per rack:

```{r sampleinfos}
result <- data.frame(table(df.samples[,"Level2_Desc"]))
colnames(result) <- c("Rack name", "Number of boxes")
pander::pander(result)
```

***Comment***: 

### Number of boxes per shelf, in each freezer:

```{r shelfinfos}
result <- table(df.samples[,c("Level1", "Freezer")])
pander::pander(result)
```

***Comment***: there is no column *ShelfBarcode* because this file will be used to generate Freezers in FreezerPro software. The column *Level1* will represent the shelf name in FreezerPro interface.

### Number of boxes per shelf, all freezers:

```{r shelfinfos2}
result <- data.frame(colSums(table(df.samples[,c("Level2","Level1")])))
colnames(result) <- "Number of boxes"
pander::pander(result)
```

***Comment***:

### Number of boxes per freezer:

```{r sheflinfos2}
result <- data.frame(colSums(table(df.samples[,c("Level2","Freezer")])))
colnames(result) <- "Number of boxes"
pander::pander(result)
```

***Comment***:

### Number of boxes per compartment:

```{r compartment}
result <- data.frame(table(df.samples[,"Level3"]))
colnames(result) <- c("Compartment name", "Number of boxes")
pander::pander(result)
```

***Comment***: only concern rack with specific compartimentation, e.g., racks of TruCulture Supernatants aliquots.

### Number of boxes per rack and per compartment:

```{r compartment2}
library(plyr)
result <- ddply(df.samples, .(Level2, Level3), nrow)
colnames(result) <- c("Level2", "Level3", "# boxes")
pander::pander(result)
```

***Comment***: 

### Number of boxes per type of box:

```{r boxtype}
result <- data.frame(table(df.samples[,c("BoxType")]))
colnames(result) <- c("BoxType", "# boxes")
pander::pander(result)
```

***Comment***:

### Number of boxes per type of box and per rack:

```{r boxtype2}
result <- ddply(df.samples, .(Level1, BoxType), nrow)
colnames(result) <- c("Level1", "BoxType", "# boxes")
pander::pander(result)
```