---
title: "Nasal swabs samples analyzes for FreezerPro import"
author: "Nolwenn Lavielle"
date: "22 août 2016"
output: pdf_document
---

```{r setup, include=FALSE}
library(plyr)
knitr::opts_chunk$set(echo = TRUE)
```

## File informations

```{r loaddataL}
path <- "/Volumes/LabExMI/Users/Nolwenn/FreezerPro/DataToImport/"
filename <- "Nasal_Swabs_rack_samples.csv"
df.samples <- read.csv(file = paste(path, filename, sep =""), 
                       header=TRUE, sep=',', stringsAsFactors = TRUE)
```

QC of a file generated to import Stool aliquot sample information into FreezerPro.

* **Filename**: `r filename`
  + **file creation date:** 2016-08-25
  + **number of rows:** `r nrow(df.samples)`
  + **number of columns:** `r ncol(df.samples)`
  + **column names:** `r names(df.samples)`

## Data informations

**Freezers**:

Expect each Freezer is assign to it respective barcode.

```{r freezerinfo}
result <- data.frame(table(df.samples[,c("Freezer")], useNA = "ifany"))
colnames(result) <- c("Freezer", "# tubes")
pander::pander(result)
```

***Comment***: only 763 lines are assigned to a Freezer. FreezerPro import will only implement 763 lines.

**Sample box type**:

Expect each sample is assign to the expected Box Type for FreezerPro.

```{r sampleinfos}
result <- data.frame(table(df.samples[,"BoxType"], useNA = "ifany"))
colnames(result) <- c("BoxType", "# tubes")
pander::pander(result)
```

***Comment***: only 763 lines are assigned to a Box Type. FreezerPro import will only implement 763 lines.

**Shelves**:

Expect each Shelf is assign to the expected barcode.

```{r shelfinfos}
result <- data.frame(table(df.samples[,"Level1"], useNA = "ifany"))
colnames(result) <- c("Level1", "# tubes")
pander::pander(result)
```

***Comment***: only 763 lines are assigned to a Shelf. FreezerPro import will only implement 763 lines.

**Racks**:
```{r rackinfos1}
result <- data.frame(table(df.samples[,"Level2"], useNA = "ifany"))
colnames(result) <- c("Level2", "# tubes")
pander::pander(result)
```

```{r rackinfos2}
result <- ddply(df.samples, .(Level1, Level2), nrow)
colnames(result) <- c("Level1", "Level2", "# tubes")
pander::pander(result)
```

```{r rackinfos3}
result <- colSums(table(df.samples[,c("Level1","Level2")], useNA = "ifany"))
pander::pander(result)
```

```{r rackinfos4}
result <- ddply(df.samples, .(Level2, Box), nrow)
colnames(result) <- c("Level2", "Box", "# tubes")
pander::pander(result)
```

```{r rackinfos5}
result <- data.frame(colSums(table(df.samples[,c("Box","Level2")])))
pander::pander(result)
```

***Comment***: only 763 lines are assigned to a Rack. FreezerPro import will only implement 763 lines.

**Box**:

```{r boxinfos}
result <- ddply(df.samples, .(Level2, Box), nrow)
colnames(result) <- c("Level2", "Box", "# tubes")
pander::pander(result)
```

<!-- **Box position**: -->

<!-- Expect each position is unique in each box. -->

<!-- ```{r posinfosL} -->
<!-- table(df.samples[,c("BoxPosition", "Box")]) -->
<!-- ``` -->

<!-- *Comment*: -->