---
title: "Stimuli samples analyzes for FreezerPro import"
author: "Nolwenn Lavielle"
date: "22 août 2016"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(plyr)
```

## File informations

```{r loaddataL}
path <- "/Volumes/LabExMI/Users/Nolwenn/FreezerPro/DataToImport/"
filename <- "TC_supernatants_samples.csv"
df.samples <- read.csv(file = paste(path, filename, sep =""), 
                       header=TRUE, sep=',', stringsAsFactors = FALSE)
```

QC of a file generated to import Stool aliquot sample information into FreezerPro.

* **Filename**: `r filename`
  + **file creation date:** 2016-08-03
  + **number of rows:** `r nrow(df.samples)`
  + **number of columns:** `r ncol(df.samples)`
  + **column names:** `r names(df.samples)`

## Data informations

### Freezers

Expect each Freezer is assign to it respective barcode.

```{r freezerinfo}
result <- data.frame(table(df.samples[,c("Freezer")], useNA = "ifany"))#, "FreezerBarcode")])
colnames(result) <- c("Freezer", "# tubes")
pander::pander(result)
```

***Comment***: missing column **FreezerBarcode**, need to be generated in Python script?

### Sample box type

```{r sampleinfos}
result <- ddply(df.samples, .(Type, BoxType), nrow)
colnames(result) <- c("Type", "BoxType", "# tubes")
pander::pander(result)
```

***Comment***: expect each sample is assign to the expected Box Type for FreezerPro.

### Shelves

Expect each Shelf is assign to the expected barcode.

```{r shelfinfos}
result <- data.frame(table(df.samples[,"Level1"], useNA = "ifany"))
colnames(result) <- c("Level1", "# tubes")
# table(df.samples[, c("ShelfBarcode","Level1")])
pander::pander(result)
```

***Comment***: missing column **ShelfBarcode**, need to be generated in Python script?

### Racks

```{r rackinfos1}
result <- data.frame(table(df.samples[,"Level2"], useNA = "ifany"))
colnames(result) <- c("Level2", "# tubes")
pander::pander(result)
```

***Comment***: missing racks:

* Donors X97>>X00 (in Shelf 1)
* Donors X48>>X50 (in Shelf 3)

```{r rackinfos2}
result <- ddply(df.samples, .(Level1, Level2), nrow)
colnames(result) <- c("Level1", "Level2", "# tubes")
pander::pander(result)
```

***Comment***: missing racks:

* Donors X97>>X00 (in Shelf 1)
* Donors X48>>X50 (in Shelf 3)

### Box infos

```{r boxinfos1}
result <- data.frame(table(df.samples[, c("Box")]))
colnames(result) <- c("Box", "# tubes")
pander::pander(result)
```

***Comment***:

### Box position

```{r posinfos}
result <- table(df.samples[,c("Position","Box")])
levs <- unique(result)
result <- factor(result, levels = sort(levs))
result <- result[result!="0"]
result <- factor(result)
barplot(table(result), col = "royalblue3", border = "royalblue3", 
        main = "Number of box per position", xlab = "Tube position", 
        ylab = "Number of box")
```

***Comment***:

### Donor data in function of volume

```{r donorinfos}
result <- data.frame(table(df.samples[,c("Volume")]))
pander::pander(result)
```

***Comment***:


### Donor infos

Number of lines: `r nrow(df.samples)`

Number of unique DonorID: `r length(unique(df.samples[,"DonorID"]))`

Number of unique OriginalDonorID: `r length(unique(df.samples[,"OriginalDonorID"]))`

Number of changed DonorID: `r abs(length(unique(df.samples[,"OriginalDonorID"]))-length(unique(df.samples[,"DonorID"])))`

***Comment***: possibly missing DonorID/OriginalDonorID. Due to freezer mapping management? Need to review rack names for supernatants?