---
title: "Stool samples analyzes for FreezerPro import"
author: "Nolwenn Lavielle"
date: "29 août 2016"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(plyr)
```

# Freezer 1532, Aliquot L

## File informations

```{r loaddataL}
path <- "/Volumes/LabExMI/Users/Nolwenn/FreezerPro/DataToImport/"
filename <- "Stools_freezer1532_L_samples.csv"
df.samples <- read.csv(file = paste(path, filename, sep =""),
                       header=TRUE, sep=',', stringsAsFactors = FALSE)
```

QC of a file generated to import Stool aliquot sample information into FreezerPro.

* **Filename**: `r filename`
  + **file creation date:** 2016-08-29
  + **number of rows:** `r nrow(df.samples)`
  + **number of columns:** `r ncol(df.samples)`
  + **column names:** `r names(df.samples)`

## Data informations

### Freezers

```{r freezerinfoL}
result <- data.frame(table(df.samples[,c("Freezer", "FreezerBarcode")]))
colnames(result) <- c("Freezer", "FreezerBarcode", "# tubes")
pander::pander(result)
```

***Comment***: only assigned to one freezer, with `r result[,3]` tubes.

### Boxes
```{r boxinfosL}
result <- ddply(df.samples, .(Box, BoxBarcode), nrow)
colnames(result) <- c("Box", "BoxBarcode", "# tubes")
pander::pander(result)
```

***Comments***: expects to have one barcode per box.

### Sample box type

```{r sampleinfosL}
result <- data.frame(table(df.samples[,"BoxType"]))
colnames(result) <- c("BoxType", "# tubes")
pander::pander(result)
```

***Comment***: should be only assigned to one box type

### Shelves

```{r shelfinfosL}
result <- ddply(df.samples, .(Level1, ShelfBarcode), nrow)
colnames(result) <- c("Level1", "ShelfBarcode", "# tubes")
pander::pander(result)
```

***Comment***: each shelf should be assign to its expected barcode

### Racks

```{r rackinfosL1}
result <- data.frame(table(df.samples[,c("Level1","Level2")]))
colnames(result) <- c("Level1", "Level2", "# tubes")
pander::pander(result)
```

***Comment***: each rack compartment should be assign to its expected shelf

```{r rackinfosL2}
result <- ddply(df.samples, .(Box,Level2), nrow)
colnames(result) <- c("Box", "Level2", "# tubes")
pander::pander(result)
```

***Comment***: each box should be assign to its respective rack compartment

### Box position

Expect each position is unique in each box.

```{r posinfosL}
result <- table(df.samples[,c("Box", "Position")])
levs <- unique(result)
result <- factor(result, levels = sort(levs))
result <- result[result != 0]
result <- factor(result)
result <- data.frame(table(factor(result)))
colnames(result) <- c("# occurences", "# tubes")
pander::pander(result)
```

***Comment***: if more than one occurence, please check the Stool Aliquot samples source file.

## Sample infos

### Tube names (barcode)

Number of lines in file: **`r nrow(df.samples)`**

Number of unique samples: **`r length(unique(df.samples[,c("Name")]))`**

***Comment***: the number of unique samples should be equal to number of lines in the file.

### Sample type

File to import into FreezerPro contains `r length(unique(df.samples[,c("Sample.Type")]))` type of sample:

```{r sampletypeL}
result <- data.frame(table(df.samples[,c("Sample.Type")]))
colnames(result) <- c("Sample.Type", "# tubes")
pander::pander(result)
```

***Comment***: the total number of tubes should be equal to the number of lines.

# Freezer 1534, Aliquot R1

## File informations

```{r loaddataR1}
path <- "/Volumes/LabExMI/Users/Nolwenn/FreezerPro/DataToImport/"
filename <- "Stools_freezer1534_R1_samples.csv"
df.samples <- read.csv(file = paste(path, filename, sep =""),
                       header=TRUE, sep=',', stringsAsFactors = FALSE)
```

QC of a file generated to import Stool aliquot sample information into FreezerPro.

* **Filename**: `r filename`
  + **file creation date:** 2016-08-29
  + **number of rows:** `r nrow(df.samples)`
  + **number of columns:** `r ncol(df.samples)`
  + **column names:** `r names(df.samples)`

## Data informations

### Freezers

```{r freezerinfoR1}
result <- data.frame(table(df.samples[,c("Freezer", "FreezerBarcode")]))
colnames(result) <- c("Freezer", "FreezerBarcode", "# tubes")
pander::pander(result)
```

***Comment***: only assigned to one freezer, with `r result[,3]` tubes.

### Boxes

```{r boxinfosR1}
result <- ddply(df.samples, .(Box, BoxBarcode), nrow)
colnames(result) <- c("Box", "BoxBarcode", "# tubes")
pander::pander(result)
```

***Comments***: expects to have one barcode per box.

### Sample box type

```{r sampleinfosR1}
result <- data.frame(table(df.samples[,"BoxType"]))
colnames(result) <- c("BoxType", "# tubes")
pander::pander(result)
```

***Comment***: should be only assigned to one box type

### Shelves

```{r shelfinfosR1}
result <- ddply(df.samples, .(Level1, ShelfBarcode), nrow)
colnames(result) <- c("Level1", "ShelfBarcode", "# tubes")
pander::pander(result)
```

***Comment***: each shelf should be assign to its expected barcode

### Racks

```{r rackinfosR11}
result <- data.frame(table(df.samples[,c("Level1","Level2")]))
colnames(result) <- c("Level1", "Level2", "# tubes")
pander::pander(result)
```

***Comment***: each rack compartment should be assign to its expected shelf

```{r rackinfosR12}
result <- ddply(df.samples, .(Box,Level2), nrow)
colnames(result) <- c("Box", "Level2", "# tubes")
pander::pander(result)
```

***Comment***: each box should be assign to its respective rack compartment

### Box position

Expect each position is unique in each box.

```{r posinfosR1}
result <- table(df.samples[,c("Box", "Position")])
levs <- unique(result)
result <- factor(result, levels = sort(levs))
result <- result[result != 0]
result <- factor(result)
result <- data.frame(table(factor(result)))
colnames(result) <- c("# occurences", "# tubes")
pander::pander(result)
```

***Comment***: if more than one occurence, please check the Stool Aliquot samples source file.

## Sample infos

### Tube names (barcode)

Number of lines in file: **`r nrow(df.samples)`**

Number of unique samples: **`r length(unique(df.samples[,c("Name")]))`**

***Comment***: the number of unique samples should be equal to number of lines in the file.

### Sample type

File to import into FreezerPro contains `r length(unique(df.samples[,c("Sample.Type")]))` type of sample:

```{r sampletypeR1}
result <- data.frame(table(df.samples[,c("Sample.Type")]))
colnames(result) <- c("Sample.Type", "# tubes")
pander::pander(result)
```

***Comment***: the total number of tubes should be equal to the number of lines.

# Freezer 1534, Aliquot R3

## File informations

```{r loaddataR3}
path <- "/Volumes/LabExMI/Users/Nolwenn/FreezerPro/DataToImport/"
filename <- "Stools_freezer1534_R3_samples.csv"
df.samples <- read.csv(file = paste(path, filename, sep =""),
                       header=TRUE, sep=',', stringsAsFactors = FALSE)
```

QC of a file generated to import Stool aliquot sample information into FreezerPro.

* **Filename**: `r filename`
  + **file creation date:** 2016-08-29
  + **number of rows:** `r nrow(df.samples)`
  + **number of columns:** `r ncol(df.samples)`
  + **column names:** `r names(df.samples)`

## Data informations

### Freezers

```{r freezerinfoR3}
result <- data.frame(table(df.samples[,c("Freezer", "FreezerBarcode")]))
colnames(result) <- c("Freezer", "FreezerBarcode", "# tubes")
pander::pander(result)
```

***Comment***: only assigned to one freezer, with `r result[,3]` tubes.

### Boxes

```{r boxinfosR3}
result <- ddply(df.samples, .(Box, BoxBarcode), nrow)
colnames(result) <- c("Box", "BoxBarcode", "# tubes")
pander::pander(result)
```

***Comments***: expects to have one barcode per box.

### Sample box type

```{r sampleinfosR3}
result <- data.frame(table(df.samples[,"BoxType"]))
colnames(result) <- c("BoxType", "# tubes")
pander::pander(result)
```

***Comment***: should be only assigned to one box type

### Shelves

```{r shelfinfosR3}
result <- ddply(df.samples, .(Level1, ShelfBarcode), nrow)
colnames(result) <- c("Level1", "ShelfBarcode", "# tubes")
pander::pander(result)
```

***Comment***: each shelf should be assign to its expected barcode

### Racks

```{r rackinfosR31}
result <- data.frame(table(df.samples[,c("Level1","Level2")]))
colnames(result) <- c("Level1", "Level2", "# tubes")
pander::pander(result)
```

***Comment***: each rack compartment should be assign to its expected shelf

```{r rackinfosR32}
result <- ddply(df.samples, .(Box,Level2), nrow)
colnames(result) <- c("Box", "Level2", "# tubes")
pander::pander(result)
```

***Comment***: each box should be assign to its respective rack compartment

### Box position

Expect each position is unique in each box.

```{r posinfosR3}
result <- table(df.samples[,c("Box", "Position")])
levs <- unique(result)
result <- factor(result, levels = sort(levs))
result <- result[result != 0]
result <- factor(result)
result <- data.frame(table(factor(result)))
colnames(result) <- c("# occurences", "# tubes")
pander::pander(result)
```

***Comment***: if more than one occurence, please check the Stool Aliquot samples source file.

## Sample infos

### Tube names (barcode)

Number of lines in file: **`r nrow(df.samples)`**

Number of unique samples: **`r length(unique(df.samples[,c("Name")]))`**

***Comment***: the number of unique samples should be equal to number of lines in the file.

### Sample type

File to import into FreezerPro contains `r length(unique(df.samples[,c("Sample.Type")]))` type of sample:

```{r sampletypeR3}
result <- data.frame(table(df.samples[,c("Sample.Type")]))
colnames(result) <- c("Sample.Type", "# tubes")
pander::pander(result)
```

***Comment***: the total number of tubes should be equal to the number of lines.

# Freezer 1535, Aliquot R2

## File informations

```{r loaddataR2}
path <- "/Volumes/LabExMI/Users/Nolwenn/FreezerPro/DataToImport/"
filename <- "Stools_freezer1535_R2_samples.csv"
df.samples <- read.csv(file = paste(path, filename, sep =""),
                       header=TRUE, sep=',', stringsAsFactors = FALSE)
```

QC of a file generated to import Stool aliquot sample information into FreezerPro.

* **Filename**: `r filename`
  + **file creation date:** 2016-08-29
  + **number of rows:** `r nrow(df.samples)`
  + **number of columns:** `r ncol(df.samples)`
  + **column names:** `r names(df.samples)`

## Data informations

### Freezers

```{r freezerinfoR2}
result <- data.frame(table(df.samples[,c("Freezer", "FreezerBarcode")]))
colnames(result) <- c("Freezer", "FreezerBarcode", "# tubes")
pander::pander(result)
```

***Comment***: only assigned to one freezer, with `r result[,3]` tubes.

### Boxes
```{r boxinfosR2}
result <- ddply(df.samples, .(Box, BoxBarcode), nrow)
colnames(result) <- c("Box", "BoxBarcode", "# tubes")
pander::pander(result)
```

***Comments***: expects to have one barcode per box.

### Sample box type

```{r sampleinfosR2}
result <- data.frame(table(df.samples[,"BoxType"]))
colnames(result) <- c("BoxType", "# tubes")
pander::pander(result)
```

***Comment***: should be only assigned to one box type

### Shelves

```{r shelfinfosR2}
result <- ddply(df.samples, .(Level1, ShelfBarcode), nrow)
colnames(result) <- c("Level1", "ShelfBarcode", "# tubes")
pander::pander(result)
```

***Comment***: each shelf should be assign to its expected barcode

### Racks

```{r rackinfosR21}
result <- data.frame(table(df.samples[,c("Level1","Level2")]))
colnames(result) <- c("Level1", "Level2", "# tubes")
pander::pander(result)
```

***Comment***: each rack compartment should be assign to its expected shelf

```{r rackinfosR22}
result <- ddply(df.samples, .(Box,Level2), nrow)
colnames(result) <- c("Box", "Level2", "# tubes")
pander::pander(result)
```

***Comment***: each box should be assign to its respective rack compartment

### Box position

Expect each position is unique in each box.

```{r posinfosR2}
result <- table(df.samples[,c("Box", "Position")])
levs <- unique(result)
result <- factor(result, levels = sort(levs))
result <- result[result != 0]
result <- factor(result)
result <- data.frame(table(factor(result)))
colnames(result) <- c("# occurences", "# tubes")
pander::pander(result)
```

***Comment***: if more than one occurence, please check the Stool Aliquot samples source file.

## Sample infos

### Tube names (barcode)

Number of lines in file: **`r nrow(df.samples)`**

Number of unique samples: **`r length(unique(df.samples[,c("Name")]))`**

***Comment***: the number of unique samples should be equal to number of lines in the file.

### Sample type

File to import into FreezerPro contains `r length(unique(df.samples[,c("Sample.Type")]))` type of sample:

```{r sampletypeR2}
result <- data.frame(table(df.samples[,c("Sample.Type")]))
colnames(result) <- c("Sample.Type", "# tubes")
pander::pander(result)
```
***Comment***: the total number of tubes should be equal to the number of lines.
