---
title: "Stimuli samples analyzes for FreezerPro import"
author: "Nolwenn Lavielle"
date: "27 oct 2016"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(plyr)
library(pander)
```

## File informations

```{r loaddataL}
path <- "/Volumes/LabExMI/Users/Nolwenn/FreezerPro/DataToImport/"
filename <- "TC_supernatants_samples_V1_all_20161027.csv"
df.samples <- read.csv(file = paste(path, filename, sep =""), 
                       header=TRUE, sep=',', stringsAsFactors = FALSE)
```

QC of a file generated to import Stool aliquot sample information into FreezerPro.

* **Filename**: `r filename`
  + **file creation date:** 2016-10-27
  + **number of rows:** `r nrow(df.samples)`
  + **number of columns:** `r ncol(df.samples)`
  + **column names:** `r names(df.samples)`

## Data informations

### Freezers

```{r freezerinfo}
result <- ddply(df.samples, .(Freezer, Freezer_Descr), nrow)
colnames(result) <- c("Freezer", "Freezer_Descr", "# tubes")
pander(result)
```

***Comment***: 

* expect each sample is assign to the expected Freezer for FreezerPro.

### Sample box type

```{r sampleinfos}
result <- ddply(df.samples, .(Sample.Type, BoxType), nrow)
colnames(result) <- c("Sample Type", "BoxType", "# tubes")
pander(result)
```

***Comment***: 

* expect each sample is assign to the expected Box Type for FreezerPro.

### Shelves

```{r shelfinfos}
result <- ddply(df.samples, .(Freezer, Level1, Level1_Descr), nrow)
colnames(result) <- c("Freezer", "Level1", "Level1_Descr", "# tubes")
pander(result)
```

***Comment***: 

* expect each sample is assign to the expected Level1 (Shelf) for FreezerPro.

### Racks

```{r rackinfos}
result <- ddply(df.samples, .(Level1, Level2), nrow)
colnames(result) <- c("Level1", "Level2", "# tubes")
pander(result)
```

***Comment***: 

* expect to have the good racks in the good shelf, for each freezer

```{r rackinfos3}
result <- ddply(df.samples, .(Level2, Level2_Descr), nrow)
colnames(result) <- c("Level2", "Level2_Descr", "# tubes")
pander(result)
```

***Comment***:

* `r nrow(result)` unique racks
* expect `r 11` unique racks for Visit 1 and `r 6` unique racks for Visit 2, in all freezers

```{r rackinfos4}
result <- ddply(df.samples, .(Level3, Level3_Descr), nrow)
colnames(result) <- c("Level3", "Level3_Descr", "# tubes")
pander(result, split.cells = 5)
```

***Comment***:

* `r length(unique(df.samples$Level3))` unique drawers
* expect `r 11*6*3` unique drawers for Visit 1 and `r 6*6*3` unique drawers for Visit 2, in all freezers

### Box infos

```{r boxinfos1}
result <- ddply(df.samples, .(Box, Box_Descr), nrow)
colnames(result) <- c("Box", "Box_Descr", "# tubes")
pander(result)
```

***Comment***:

* `r length(unique(df.samples$Box))` unique boxes
* expect `r 11*40*3` unique boxes for Visit 1 and `r 6*3*40` unique boxes for Visit 2, in all freezers

### Box position

```{r posinfos}
result <- table(df.samples[,c("Position","Box")])
levs <- unique(result)
result <- factor(result, levels = sort(levs))
result <- result[result!="0"]
result <- factor(result)
result <- as.data.frame(table(result))
colnames(result) <- c("Duplicated position per box", "# tubes")
pander(result)
```

***Comment***: 

* expect to have unique positions in each box

### Donor data in function of volume

```{r donorinfos}
result <- data.frame(table(df.samples[,c("Volume")]))
colnames(result) <- c("Volume", "# tubes")
pander(result)
```

***Comment***:

* each tubes should contain a volume of 400.0 µL

### BatchID info

```{r batchinfos}
result <- ddply(df.samples, .(VisitID, BatchID), nrow)
colnames(result) <- c("VisitID", "BatchID", "# tubes")
pander(result)
```

***Comment***: 

* Total number of tubes: `r sum(result[,3])`
* donors were included in two batches in Visit 1 and Visit 2.

### More donor infos

* Number of lines: `r nrow(df.samples)`
* Number of unique DonorID: `r length(unique(df.samples[,"DonorID"]))`
* Number of unique Sample Source: `r length(unique(df.samples[,"Sample.Source"]))`
* Number of unique Name: `r length(unique(df.samples[,"Name"]))`
* Visit number: `r unique(df.samples$VisitID)`
* ***Comment***: 

    * expect 1.000 DonorID and Sample Source, and 1 Name per line, for Visit 1
    * expect 500 DonorID and Sample Source, and 1 Name per line, for Visit 2

```{r donorsub}
sdf <- subset(df.samples, DonorID > 5000)
result <- ddply(sdf, .(DonorID, AliquotID), nrow)
colnames(result) <- c("DonorID", "AliquotID", "# tubes")
pander(result)
```

***Comment***: 

* `r length(unique(sdf$DonorID))` DonorID were replaced, expect 40 tubes per DonorID and AliquotID