---
title: "TruCulture Trizol samples for FreezerPro import"
author: "Nolwenn Lavielle"
date: "25 août 2016"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## File informations

```{r loaddata}
path <- "/Volumes/LabExMI/Users/Nolwenn/FreezerPro/DataToImport/"
filename <- "TC_Trizol_rack_samples.csv"
df.samples <- read.csv(file = paste(path, filename, sep =""), 
                       header=TRUE, sep=',', stringsAsFactors = FALSE)
```

QC of a file generated to import TruCulture Trizol sample information into FreezerPro.

* **Filename**: `r filename`
  + **file creation date:** 2016-08-25
  + **number of rows:** `r nrow(df.samples)`
  + **number of columns:** `r ncol(df.samples)`
  + **column names:** `r names(df.samples)`
  
The file to import contains source tubes used for stimulation analyzis.

## Data informations

**Freezers**:

```{r freezerinfo}
library(plyr)
result <- ddply(df.samples, .(Freezer, FreezerBarcode), nrow)
colnames(result) <- c("Freezer", "FreezerBarcode", "# tubes")
pander::pander(result)
```

Each freezer is assign to the expected barcode.

**Box type**:

```{r sampleinfos}
result <- data.frame(table(df.samples[,"BoxType"]))
colnames(result) <- c("BoxType", "# tubes")
pander::pander(result)
```

Each sample is assign to the expected box type for FreezerPro.

**Shelves**:
```{r shelfinfos2}
pander::pander(table(df.samples[,"Level1"]))
shelves <- ddply(df.samples, .(ShelfBarcode, Level1), nrow)
colnames(shelves) <- c("ShelfBarcode", "Level1", "# tubes")
pander::pander(shelves)
```

Each shelf is assign to the expected barcode.

**Racks**:
```{r rackinfos}
result <- data.frame(table(df.samples[,"Level2"]))
colnames(result) <- c("Level2", "# tubes")
pander::pander(result)
```

```{r rackinfos2}
result <- table(df.samples[,c("Level2","ShelfBarcode")])
levs <- unique(result)
result <- factor(result, levels = sort(levs))
result <- result[result!="0"]
result <- factor(result)
barplot(table(result), col = "royalblue3", border = "royalblue3", 
        main = "Number of tube per rack", xlab = "Number of tube per rack", 
        ylab = "Number of rack")
```

```{r rackinfos3}
result <- data.frame(colSums(table(df.samples[,c("Level2","ShelfBarcode")])))
colnames(result) <- "# tubes"
pander::pander(result)
```

### Box position

```{r posinfos}
result <- table(df.samples[, c("Box", "Position")])
levs <- unique(result)
result <- factor(result, levels = sort(levs))
barplot(table(result), col = "royalblue3", border = "royalblue3", 
        main = "Number of tube per box", xlab = "Number of tube per box", 
        ylab = "Number of box")
```

## Sample infos

### Number of tubes in funciton of StimulusID and VisitID

```{r stimidvsvisidinfos}
subdf <- df.samples[, c("VisitID", "StimulusID")]
lvls <- unique(subdf$VisitID)
subdf$VisitID <- factor(subdf$VisitID, levels = lvls)
result <- table(subdf)
pander::pander(result)
```


***Comment***:

* first line: StimulusID
* first column: VisitID

### Number of tubes in function of StimulusID and BatchID

```{r stimidvsbatidinfos}
result <- table(df.samples[, c("BatchID", "StimulusID")])
pander::pander(result)
```

***Comment***:

* first line: StimulusID
* first column: BatchID

### Number of tubes in function of BatchID and VisitID
```{r batidvsvisidinfos}
result <- ddply(df.samples, .(VisitID, BatchID), nrow)
colnames(result) <- c("VisitID", "BatchID", "# tubes")
```

## DonorIDscanned infos

* `r length(unique(df.samples[,"DonorIDscanned"]))` unique DonorIDscanned in file. 
* `r length(unique(df.samples[,"barcode"]))` unique barcode in file.

***Comment***: *DonorIDscanned* column is a copy of column *barcode*.